---
title: "A25_Hoermann"
output: pdf_document
---
```{r}
library(lattice)
library(latticeExtra)
c = sort(rnorm(5))
c
```
  1. unbiasedness
  2. efficiency
  3. consistency
  4. sufficiency
  5. robustness
  
## arithmetic mean
```{r}
stripplot(c) + as.layer(stripplot(mean(c), col = "red"))
```
  1. unbiased
  2. efficient
  3. consistent
  4. very sufficient, every x is considered
  5. outlayers: problem, not robust
  
## median
```{r}
stripplot(c) + as.layer(stripplot(median(c), col = "red"))
```
  1. biased
  2. efficient
  3. consistent
  4. very insufficient, only one value is considered (and its ordinal pos)
  5. outlayers are not a problem, more robust than arith. mean
  
## midrange
```{r}
est = (c[1] + c[5]) / 2
stripplot(c) + as.layer(stripplot(est, col = "red"))
```
  1. biased
  2. inefficient
  3. consistent
  4. also rather insufficient
  5. not so robust
  
## 5 values, sorted & weighted
```{r}
est = sum(c(1:3,2:1) * c) / 9
stripplot(c) + as.layer(stripplot(est, col = "red"))
```
  1. biased
  2. inefficient
  3. inconsistent
  4. sufficient, every x is considered
  5. rather robust, outlayers have low weight