---
title: "A31_Hoermann"
author: "Paul Hörmann"
date: "12/5/2019"
output: pdf_document
header-includes:
  - \usepackage{float}
  - \floatplacement{figure}{H} 
fig_caption: yes
---
```{r}
library(data.table)
library(zoo)
```
```{r}
set.seed(1)
v3 = rnorm(n = 50, mean = 30, sd = 3)
v4 = runif(n = 50, min = 20, max = 40)
```
```{r}
head(data.table(v3=v3, v4=v3))
tail(data.table(v3=v3, v4=v3))
```
```{r}
h3 = hist(v3)
```
```{r}
h4 = hist(v4)
```

## Test for uniform distribution of h3
```{r}
bincount = length(h3$counts)
chisq.test(h3$counts, p=rep(1/bincount, bincount))
```

P value of around 0 seems valid, the values are indeed not uniformly distributed, 

### Function to get p vector for histogram breaks
```{r}
getProbs = function (breaks, mean, sd) {
  sub = 0
  len = length(breaks) - 1
  p = integer(len)
  for (i in 1:(len - 1)) {
    p[i] = pnorm(q = breaks[i + 1], mean = mean, sd = sd) - sum(p)
  }  
  p[len] = 1 - sum(p)
  p
}
```

## Test for normal distribution of h3
```{r}
chisq.test(h3$counts, p = getProbs(h3$breaks, 30, 3))
```

P value of 0.6 makes sense, as the values are indeed normally distributed but rather heavy on the right side, as visible from the histogram.

## Test for uniform distribution of h4
```{r}
bincount = length(h4$counts)
chisq.test(h4$counts, p=rep(1/bincount, bincount))
```

P value of around 0.4 makes sense, though randomness got a hit on the equalness of distribution.

## Test for normal distribution of h4
```{r}
chisq.test(h4$counts, p = getProbs(h4$breaks, 30, 3))
```

P value of basically 0 makes sense, as the values are not normally distributed.