---
title: "A12_Hoermann"
author: "Paul Hörmann"
date: "11/3/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Function definition
```{r}
i = c(1:10000)
x = c(1:9)
calcor <- function(i) {
  y = sample(x, 9);
  cor(x, y, method="spearman")
}
rk = sapply(i, calcor)
```

## Summary
```{r}
summary(rk)
```
## Standard deviation
```{r}
sd(rk)
```

## Density plot
```{r}
plot(density(rk))
```

## Transform values
```{r}
transform <- function(i) {
  i * sqrt(7 / (1 - i^2))
}
rkt = sapply(rk, transform)
```

## Summary
```{r}
summary(rkt)
```

## Standard deviation
```{r}
sd(rkt)
```

## Density plot (original scaling)
```{r}
plot(density(rkt))
```

## Density plot (adjusted scaling)
```{r}
plot(density(rkt), ylim=c(0,1.5), xlim=c(-1, 1))
```

As visible from above, the transformation spreads the values further out, where the spread is increasing by the size of the coefficient. Meaning that the farther the values are from the center, the more the transformation moves them away from the center. In other words: it flattens the distribution.
