---
title: "Endprojekt_Hoermann"
author: "Paul Hörmann"
date: "1/12/2020"
output: pdf_document

---

## Acknowledgement
If not otherwise stated a error of 5% is used. For all Tests / Overviews data was removed if the attribute of interest had an unknown value. As we are taking a look at if the loan was given or not, data where it's unknown has been removed right away.

## Overview
```{r, echo=FALSE}
# Preparation
library(gdata)
library(data.table)
library(plyr)
library(dplyr)
library(ggplot2)
library(scales)
library(corrplot)
library(RColorBrewer)
library(xtable)
```



```{r, echo=FALSE}
setwd("~/git/fhhgb_ws19/ASC/r/project/")
source = data.table(read.xls("./deposit.xlsx"))
head(source)

source = droplevels(source %>% filter(source$y != 'unknown'))
source$private_loan = +(source$loan=="yes")
source$signed_deposit_enc = +(source$y=="yes")
source$housing_loan = +(source$housing =="yes")
source$signed_deposit =  source$y

source %>% group_by(signed_deposit) %>% add_tally(name = "Count") %>%
  ggplot(., aes(x = signed_deposit, y = Count, fill = signed_deposit)) +
  geom_bar(stat = "identity") +
  geom_text(aes(x = signed_deposit, y = Count, label = Count),
            position = position_dodge(width = 1),
            hjust = -1) + 
  scale_y_continuous(labels = comma) +
  coord_flip()
```

## Correlation Analysis
```{r, echo=FALSE}
num_source = source %>% filter(pdays != 999) %>%
  select(signed_deposit_enc, housing_loan, private_loan,
         age, duration, campaign, pdays, previous,
         emp.var.rate, cons.price.idx, cons.conf.idx,
         euribor3m, nr.employed)

corr = cor(num_source$signed_deposit_enc, as.matrix(num_source))
corrplot(corr, type = "upper", order = "original",
         col = brewer.pal(n = 4, name = "RdYlBu"))
```

As Visible above there are 5 main factors correlating with the signage of a deposit. Positively correlating is the duration of the call, the consumer price index and the consumer confidence index. Negatively correlating is the 3 month euribor and the number of employed.

Below you can see the values ordered by their correlation.

```{r, echo=FALSE}
corr_tab = as.data.table(cor(
  as.matrix(num_source$signed_deposit_enc),
  as.matrix(num_source)
  ))
as.data.table(c(corr_tab)[order(-corr_tab^2)])
```

Now we take a look at the coefficient of determination, to find out how much influence those values really have.

```{r, echo=FALSE}
summary(lm(source$signed_deposit_enc~source$nr.employed))$r.squared
```
```{r, echo=FALSE}
summary(lm(source$signed_deposit_enc~source$euribor3m))$r.squared
```
```{r, echo=FALSE}
summary(lm(source$signed_deposit_enc~source$duration))$r.squared
```
```{r, echo=FALSE}
summary(lm(source$signed_deposit_enc~source$cons.price.idx))$r.squared
```
```{r, echo=FALSE}
summary(lm(source$signed_deposit_enc~source$cons.conf.idx))$r.squared
```

## Taking a look at the most important factors

```{r, echo=FALSE}
source %>% ggplot(., aes(x = duration, fill = signed_deposit)) +
  geom_histogram(bins = 10) +
  stat_bin(bins = 10)
```

As you can see, the ratio of yes to no increases the longer the duration of the call was.

```{r, echo=FALSE}
kruskal.test(source$signed_deposit~ source$signed_deposit_enc)
```

And the test shows, that the influence is statistifically significant.

```{r, echo=FALSE}
cleaned_poutcome = droplevels(source %>% filter(source$poutcome != 'unknown'))
cleaned_poutcome %>% count(poutcome, signed_deposit) %>%
  group_by(poutcome) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = poutcome,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()
```

Especially people previously signed tend to do the same again.

```{r, echo=FALSE}
kruskal.test(cleaned_poutcome$signed_deposit~ cleaned_poutcome$poutcome)
```

Which is also statistically significant.

```{r, echo=FALSE}
cleaned_marital = droplevels(source %>% filter(source$marital != 'unknown'))
cleaned_marital %>% count(marital, signed_deposit) %>%
  group_by(marital) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = marital,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent)
```


```{r, echo=FALSE}
cleaned_jobs = droplevels(source %>% filter(source$job != 'unknown'))
cleaned_jobs %>% count(job, signed_deposit) %>%
  group_by(job) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = job,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()
```


```{r, echo=FALSE}
cleaned_edu = droplevels(source %>% filter(source$education != 'unknown'))
cleaned_edu %>% count(education, signed_deposit) %>%
  group_by(education) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = education,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()
```


As you can see from the three previous graphs students, retired people and also illiterate people tend more to sign a deposit than others, whereas marital status has no big influence.

```{r, echo=FALSE}
converted = source
converted$previous = as.factor(converted$previous)
converted %>% count(previous, signed_deposit) %>%
  group_by(previous) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = previous,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()
```



```{r, echo=FALSE}
emp_rate_encoded = source
emp_rate_encoded$emp_rate = apply(source, 1, function(line) {
  if (as.numeric(line["emp.var.rate"]) > 0) {
    "+"
  } else {
    "-"
  }
})
emp_rate_encoded %>% count(emp_rate, signed_deposit) %>%
  group_by(emp_rate) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = emp_rate,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()
```

As already seen before, the employment rate has big influence on wether people tend to sign or not.

```{r, echo=FALSE}
source %>%
  ggplot(., aes(x = age)) +
  geom_histogram(binwidth = 10, fill = "orange") +
  stat_bin(binwidth = 10, aes(y = ..count../sum(..count..),
                              label=percent(..count../sum(..count..))),
           geom = "text")
```

```{r, echo=FALSE}
age_enc = droplevels(source %>% filter(source$age != 'unknown'))
age_enc$age_encoded = apply(source, 1, function(line) {
  age = as.numeric(line["age"])
  if (age  < 25) {
    "<25"
  } else if (age < 35) {
    "25-34"
  } else if (age < 45) {
    "35-44"
  } else if (age < 55) {
    "45-54"
  } else if (age < 65) {
    "55-64"
  } else {
    "64>"
  }
})
age_enc %>% arrange(age) %>% count(age_encoded, signed_deposit) %>%
  group_by(age_encoded) %>%
  mutate(Ratio = prop.table(n)) %>%
  ggplot(., aes(x = age_encoded,
                y = Ratio, fill = signed_deposit)) +
  geom_col() +
  geom_text(aes(label = percent(Ratio)), position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent) +
  coord_flip()

```
```{r, echo=FALSE}
grouped_data = age_enc %>%
  group_by(age_encoded) %>%
  count(signed_deposit_enc) %>%
  mutate(Ratio = prop.table(n)) %>% filter(signed_deposit_enc== 1)
  
new_age <- age_enc %>% filter(!(age_encoded == "25-34" & signed_deposit_enc == 0))

kruskal.test(age_enc$signed_deposit_enc~age_enc$age_encoded)
```

The age more or less matches the job, meaning younger students and older retired people are more likely to sign a deposit.
